---
title: "crisprDesignAux: auxiliary functions to the crisprDesign package"
output: 
  github_document:
    toc: true
---

```{r, echo=FALSE, results="hide"}
options("knitr.graphics.auto_pdf"=TRUE, eval=TRUE)
```

Authors: Jean-Philippe Fortin

Date: Sept 12, 2022

# Overview

`crisprDesignAux` 


# Installation


`crisprDesignAux` is supported for macOS, Linux and Windows machines.
It was developed and tested on R version 4.2.1, and can be installed from 
the Bioconductor devel branch by typing the following commands inside 
of an R session:

```{r, eval=FALSE}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install(version="devel")
BiocManager::install("crisprDesignAux")
```

# Converting a GuideSet object to a BED file

We load `crisprDesignAux` in the usual way:

```{r, warnings=FALSE, message=FALSE}
library(crisprDesignAux)
```

# GuideSet objects as SQLite databases

```{r, warnings=FALSE, message=FALSE}
library(crisprDesign)
data(guideSetExampleFullAnnotation)
dbfile <- tempfile() 
GuideSetToSqlite(guideSet=guideSetExampleFullAnnotation,
                 dbfile=dbfile)
```

We can also convert back a SQLite database into a GuideSet object:

```{r, warnings=FALSE, message=FALSE}
library(crisprBase)
library(BSgenome.Hsapiens.UCSC.hg38)
bsgenome <- BSgenome.Hsapiens.UCSC.hg38
data(SpCas9, package="crisprBase")
gs <- SqliteToGuideSet(dbfile=dbfile,
                       bsgenome=bsgenome,
                       crisprNuclease=SpCas9)
```


The `dbplyr` package is useful to interact with SQLite objects as if they were regular data.frames:

```{r}
library(dbplyr)
con <- DBI::dbConnect(RSQLite::SQLite(), dbname = dbfile)
gs <- tbl(con, from="primary")
```

Suppose that we wanted to filter GC content

```{r}
gs <- filter(gs, percentGC>=20 & percentGC<=80)
```


# License

The project as a whole is covered by the MIT license. 

# Reproducibility

```{r}
sessionInfo()
```




